Compositional equivalences based on Open pNets

### 2020-04-03 2016-Weak-FH-Bisim/WeakBisim.tex
moved Fig 10, and added D.1
replaced Fig 7 by Fig 10,
added some first content to appendix D.1

\begin{figure}[h]
   \centerline{\includegraphics[width=11cm]{XFIG/SimpleProtImpl-WOA}}
  \caption{Weak Open Automaton of the implementation}
   \label{SimpleProtCounter:ImplWOA}
\end{figure}
\RAB{In the above example, notations should be corrected once  figure \ref{SimpleProtCounter:ImplWOA} selected}

@@

        \subsection{\TODO{Details of the Bisimulation Checking}}

@@

%% \section{Examples of Lotos laws}
%% Possible Lotos small examples:

%% Strong bisim:\\
%% 1) Hiding:\\
%% \centerline{hide \{g\} in a;B  ==  a; hide \{g\} in B  iff gatename(a)$\neq$g}\\
%% \centerline{hide \{g\} in a;B  ==  i; hide \{g\} in B  iff gatename(a)$=$g}
%% 2) Disabling:\\
%% \centerline{B1[>(B2[>B3) == (B1[>B2)[>b3}\\
%% \centerline{(B1[>B2)[]B3 == B1[>B2}\\
%% \centerline{B[>stop == B}\\
%% \centerline{stop[>B == B}\\
%% \centerline{exit(...)[>B == exit(...)[]B}\\
%% 3) Enabling:\\
%% \centerline{B1>>(B2>>B3) == (B1>>B2)>>b3}\\
%% \centerline{B>>stop == B|||stop}\\
%% \centerline{stop>>B == stop}\\
%% \centerline{exit>>B == i;B}\\
%% 4) Choice:\\
%% \centerline{B1[](B2[]B3) == (B1[]B2)[]b3}\\
%% \centerline{B1[]B2 == B2[]B1}\\
%% \centerline{B[]stop == B}\\
%% \centerline{B[]B == B}\\

%% 5) Others:\\
%% \centerline{B1|[]|B2 == B1|||B2}\\

%% Weak congruence:\\
%% \centerline{a;i;B == a;B}\\
%% \centerline{B[]i;B == i;B}\\
%% and many others, often not easy to express without syntax for set operations,
%% like e.g.:
%% \centerline{}

%% Weak equivalence:\\
%% \centerline{i;B == B}

>>>>

%\begin{figure}[h]
  % \centerline{\includegraphics[width=11cm]{XFIG/SimpleProtImpl-WOA}}
 % \caption{Weak Open Automaton of the implementation}
 %  \label{SimpleProtCounter:ImplWOA}
%\end{figure}
\RAB{In the above example, notations should be corrected once  figure \ref{SimpleProtCounter:ImplWOA} selected}

\begin{figure}[h]
   \centerline{\includegraphics[width=11cm]{XFIG/SimpleProtImpl-WOA2}}
  \caption{Weak Open Automaton of the implementation}
   \label{Appendix:ImplOA2}
\end{figure}

@@

        \subsection{Details of the Bisimulation Checking}

We reacall here the realtion $\mathcal{R}$ that is the candidate for our weak bisimulation relation:

\bigskip
  \begin{tabular}{|c|c|l|}
\hline
    Spec state & Impl state & Predicate\\
    \hline
    b0 & $000$ & True\\
    b0 & $202$ & True\\
    b1 & $100$ & $\texttt{b1\_msg = s1\_msg} \land \texttt{b1\_ec = s1\_ec}$\\
    b1 & $210$ & $\texttt{b1\_msg = m1\_msg} \land \texttt{b1\_ec = m1\_ec}$\\
    b1 & $220$ & $\texttt{b1\_msg = s2\_msg} \land \texttt{b1\_ec = s2\_ec}$\\
    b1 & $201$ & $\texttt{b1\_msg = r1\_msg} \land \texttt{b1\_ec = r1\_ec}$\\
    \hline
    \end{tabular}

\bigskip
Considering the first triple <b0, 000, True>, we will prove the following properties, in which $OT<<WOT$ means that the (strong) open transition $OT$ is covered, in the sense of definition \ref{def-Weak-bisim} by the weak transition $WOT$ (it could be a set, but this will not be used here):

\bigskip
$SS_1 << WI_1$

$SS_2 << WI_2$

$SS_3 << WI_3$

\smallskip
$SI_1 << WS_1$

$SI_2 << WS_2$

$SI_3 << WS_3$

         Note: if we were using the alternative Weak bisim from Appendix \ref{app-WFH-equiv}, Lemma \ref{lem-rel-OT-WOT}, we would have a lot more transitions to examine, as we  have 4 weak transitions for $b0$ in the specification weak automaton, but 7 WOTs from 000 in the implementation automaton.

         And these numbers raise faster for other states, e.g. 13 WOTs for state 100.

@@
